\section{Literature Review}

At least since the 1940s, social scientists have relied on survey research to understand the factors affecting voting behavior, yet only recently have scholars begun to use experimental and observational evidence to gain "causal leverage for analyses of voting behavior." \cite{bartels_larry_m._study_2010} Early studies of voting behavior established that although individual vote choice is susceptible to election-year specific shocks, for example an unusually  popular presidential candidate or war-time discontent, the way an individual votes in most elections is a function of their personal identity characteristics. \cite{ConverseNormalVote}. The most significant determinants of long-term voting behavior according to this line of research include party identification, ethnicity, gender, age, religion, education, and occupation. (Lazerfeld1944,Berelson1954,Campbell1960,Stanley2006) Noteworthy too are the factors these studies did \textit{not} find significant for long-term voting behavior: preferences about political issues, for example, economic self-interest. These results, which have passed extensive scrutiny and replication (Nie1976,Smith1989,LewisBeck2008), have nonetheless faced significant challenges in the past decade, and some of what we thought we knew about voting behavior is being upended. As far as the determinants of life-long voting behavior, issues and economic interest are gaining renewed appreciation. \cite{Ansolabehere_Snyder_Rodden} show that the apparent incoherence of individual issue attitudes may largely be a result of measurement error, and that by averaging multiple question responses one gets a more stable estimate of individual issue attitudes, which become nearly as predictive of voting behavior as partisan identification. Meanwhile, \cite{Gelman2009} use WHAT KIND OF survey data to establish that income \textit{can} be an important determiner of individual vote behavior, but its predictive power depends greatly on geography: in poor states like Alabama those who make little vote very differently from those who make a lot, while in rich states like Connecticut the difference is barely present. The primary innovation of both these papers is that they make compelling arguments for the use of data analysis techniques not normally used within the strand of survey research concerned with voting behavior. Other recent papers have proposed to use entirely different data sources based on experimental or observational data to answer typical survey questions. \cite{Hersh2015}, for example, use highly dis-aggregated registration, census, and election returns to build on \cite{Gelman2009}, showing that income is a significant determiner of voting behavior only in Congressional districts characterized by a high degree of racial diversity.  Experimental work has shown that voting behavior may be how issues are framed in the media,(Iyengar) by the quantity and quality of advertising (Gerber), and by emotional triggers such as anger. (Valentino2012)

If the empirical literature on voting behavior has until recently tended to downrate the importance of individual economic context for voting behavior, the same is not true for the theoretical literature.

Our work is also related to the literature on prospective and retrospective voting.