Although our matching methods acheived balance on almost all covariates the literature has generally considered significant at predicting long-term voting behavior, treated units had an average African-American population of about 6\% while control units had an average African-American population of about 4\%, and this difference was statistically significant. One concern is that changes in racial voting behavior between the 2000 and 2004 election could explain some of our results. The fact that the black population is so small in both groups decrease this possibility, however as a precaution we provide here a brief analysis of exit poll and turnout data for each state and each election year, in order to estimate how changes in African-American and non-African American voting behavior might effect our results. According to these exit polls, Gore was supported by 90.5\% of black voters and 51.4\% of other voters, while Kerry was suppoted by only 83.4\% of black voters and 47.3\% of other voters.\footnote{Here all figures correspond to two-party vote, consistent with the approach taken throught  the paper. Individuals who say they supported Nader or some other candidate are therefore dropped in our analysis of these exit polls.}  At the same time, about 53\% of the black population and 56\% of the non-black population voted in 2000, while 61\% of the black population and 66\% of the non-black population voted in 2004. Assuming that these estimates of average turnout and support by race are the same in treated and control units, we can estimate the difference-in-difference purely due to racial imbalance as -0.0007, two orders of magnitude smaller than our effect. \footnote{Formally, we use the following equation: $$(\frac{ T_B^{04} D_B^{04} +  T_O^{04}  D_O^{04}}{ T_B^{04} +  T_O^{04}} - \frac{ T_B^{00} D_B^{00} +  T_O^{00}  D_O^{00}}{ T_B^{00} +  T_B^{00}}) - (\frac{ C_B^{04} D_B^{04} +  C_O^{04}  D_O^{04}}{ C_B^{04} +  C_B^{04}} - \frac{ C_B^{00} D_B^{00} +  C_O^{00}  D_O^{00}}{ C_B^{00} +  C_B^{00}}) $$ 
Here, $T_B^{0X}$ is the fraction of the black population that voted in the year $200X$ multiplied by the fraction of the population that is black in the treated units, while $T_O^{0X}$ indicates the fraction of the population that voted among other races times the fraction of the population that is not-black.  $D_B^{0X}$, $D_O^{0X}$ indicates the proportion of blacks and non-blacks who supported the democratic Presidential candidate in year $XX$. $C_B^{XX}$ is the fraction of the black population that voted in the year $200X$ multiplied by the fraction of the population that is black in the control units, with $C_O^{XX}$ is defined analogously.}  Thus, racial imbalance between treated and control does not seem to pose a serious threat to our analysis of voting behavior.
